Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-03-17 2017-Xudong-SMT/OpenPNets-SMT.tex
Added todos for the next week

\section{Running Examples}
\TODO{Graph of two examples: CCS a.P||b.Q [DONE] and LOTOS (P>>Q)>>R}

@@

\QIN{There are several former papers already have illustrated many examples in closed pNets show that pNets can properly simulate the original construct. In this section, we encode the operators from other algebras into the pNets present the feature of the open pNet. They will be the running examples in the whole paper. }

@@

\subsection{Presentation of algebra}
\QIN{Before the encoding, the presentation of the pNet should be given first. We can divide the presentation into two parts:}
\begin{itemize}
	\item Sorts: Constants sets of the algebra, types of the data and actions.
	\item Operators: Operators comes from other algebras,  constructors for the parameterized actions.
\end{itemize}

@@

2d)
\ERIC{Optionally, simplify the predicate by eliminating the unnecessary intermediate variables, that were produced as fresh local variables of synchronisation vectors, and fresh result variables of intermediate OTs. In the resulting predicate the only significant variables are :\\
- the input variables of pLTS transitions\\
- the actions of holes\\
- the result action at toplevel.}

@@

\TODO{Xudong: Detailed description of the implementation}

@@

\ERIC{
=> Context VCE, ref to FASE paper\\
=> Current prototype: programatic creation of pNet objects, through the pNet API in VCE. On the middle term, this should be compiled from some language or graphical formalism.\\
=> Open transitions are computed as a direct implementation of the algorithm above. Steps 2a-2b are merged: at each pNet node, after application of rule Tr2, the resulting OT is built from the premisses, without explicitely constructing the deduction tree. \\
=> Variable names are generated for all ``fresh'' and ``clone''
operations, using structured variable names ensuring uniqueness of
fresh names, but also reasonable readability of these names for
debugging purposes.\\
=> Assignements\\
=> Satisfiability check is done only at toplevel of the deduction tree construction. An alternative would be to submit the satisfiability check to the SMT solver at each level of the tree construction, potentialy reducing the overall number of combinations. But submission to the SMT engine is costly, and more complexity analysis is required before deciding if this would be worthwhile.\\
=> Simplification is not yet implemented. It is not strictly required for the Open Automaton construction, but it will be critical later for predicate comparison in the bisimulation algorithm.}

@@

>>>>

\section{Running Examples}
Several publications \cite{PDP2015,FORTE2016} already have introduced
many examples of pNets, encoding
operators of various classical process algebras, or more complex
synchronisation structures in distributed or parallel languages.
In this section, we use two process expressions, respectively from CCS
and from Lotos, to illustrate different features of pNets. They will
serve as running examples in the whole paper.

\TODO{Graph of two examples: CCS a.P||b.Q [DONE] and LOTOS (P>>Q)>>R}

@@

\TODO{Xudong: correction of the 2 figures (CCS and LOTOS). Then Eric will write / rewrite the explanation text}

@@

\subsection{Presentation of algebra}
\TODO{Eric: write an introductory paragraph}

\QIN{Before the encoding, the presentation of the pNet should be given first. We can divide the presentation into two parts:}
\begin{itemize}
	\item Sorts: Constants sets of the algebra, types of the data and actions.
	\item Operators: Operators comes from other algebras,  constructors for the parameterized actions.
\end{itemize}

@@

@@

\TODO{Xudong: Missing a general summary before going into details. You
  can get inspiration from the following (reasonnable level of
  abstraction):}
\ERIC{
=> Context = use the existing software architecture from VCE (ref to \cite{FASE} paper)\\
=> Current prototype: programatic creation of pNet objects, through the pNet API in VCE. On the middle term, this should be compiled from some language or graphical formalism.\\
=> Open transitions are computed as a direct implementation of the algorithm above. Steps 2a-2b are merged: at each pNet node, after application of rule Tr2, the resulting OT is built from the premisses, without explicitely constructing the deduction tree. \\
=> Variable names are generated for all ``fresh'' and ``clone''
operations, using structured variable names ensuring uniqueness of
fresh names, but also reasonable readability of these names for
debugging purposes.\\
=> Assignements\\
=> Satisfiability check is done only at toplevel of the deduction tree construction. An alternative would be to submit the satisfiability check to the SMT solver at each level of the tree construction, potentialy reducing the overall number of combinations. But submission to the SMT engine is costly, and more complexity analysis is required before deciding if this would be worthwhile.\\
}

@@

@@

\TODO{Conclusion: what you have accomplished, clearly state your
  contributions, and what is delivered at the end of your internship
  work}

\TODO{Discussion: next steps: 1) what is left as open questions on the
  algorithm itself, what you have learned (is Z3 useful and efficient,
  is it the right tool ?). 2) next important goal is bisimulation
  checking, what is neded for that (formalize the algo, define and
  implement simplification)}

=> Simplification is not yet implemented. It is not strictly required
for the Open Automaton construction, but it will be critical later for
predicate comparison in the bisimulation algorithm.

\ERIC{Optionally, simplify the predicate by eliminating the unnecessary intermediate variables, that were produced as fresh local variables of synchronisation vectors, and fresh result variables of intermediate OTs. In the resulting predicate the only significant variables are :\\
- the input variables of pLTS transitions\\
- the actions of holes\\
- the result action at toplevel.}
